---
pagetitle: "Demo: ninja scaffold"
output:
  xaringan::moon_reader:
    css: [default, ninjutsu, custom.css, custom-fonts.css]
    self_contained: yes
    lib_dir: libs
    seal: false
    nature:
      ratio: "16:9"
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---
layout: true

```{r, prep-chunks, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE, warning = FALSE,
  fig.retina = 3
)
```

```{r, prep-pkgs}
library(dplyr)
library(knitr)
library(ggplot2)
library(icon)
```

```{r, prep-plot}
plot <- ggplot(iris, aes(Sepal.Width, Sepal.Length, colour = Species)) +
  geom_point()
```

---
class: split-title hide-slide-number

.row[.content[
# `r fa("user-ninja", size = 3)`
]]

.row[.content[
# Demo: Ninja Scaffold
## Splitting [{xaringan}](https://slides.yihui.org/xaringan/#1) slides into sections
### Adapting [Emi Tanaka](https://emitanaka.org/)'s [Ninjutsu](https://emitanaka.org/ninja-theme/themes/kunoichi/kunoichi-theme-example.html#7)

`r fa('twitter')` [mattdray](https://twitter.com/mattdray)
`r fa('github')` [slide source](https://github.com/matt-dray/ninja-scaffold/)
`r fa('globe')` [blogpost](https://www.rostrum.blog/2020/03/22/ninja-scaffold/) 
]]

---
class: split-main1

.row[.content[
### Header and footer with main body between
]]

.row[.content[

```{r, plot-large, fig.width=16}
print(plot)
```
]]

.row[
]

---
class: split-main2

.row[.content[
### Main body split in two horizontally
]]

.row[.content[
This slide is split into four rows that are all 100% of the width of the page:

* the title (top) and footer (bottom) bars
* the main body area (this the upper row, there's a plot in the one below)

]]

.row[.content.center[
```{r, plot-wide, fig.width=15, fig.height=3}
print(plot)
```
]]

.row[
]

---
class: split-main2

.row[.content[
### Vertical split in the second row of the main body
]]

.row[.content[
This is just like the previous slide, but with one important difference: the lower row of this main body area is split in half vertically.

This makes it easier to palace the table to the left and the icon to the right.
]]

.row[.content[
.split-two[
.column[.content[
`r kable(head(iris), format = "html")`
]]
.column.center[.content[
`r fa("r-project", size = 5)` 
]]
]
]]

.row[
]

---
class: split-title hide-slide-number with-thick-border border-black

.row[.content[
]]

.row[.content[
# Class `split-title`
]]

---
class: split-main1 with-thick-border border-black

.row[.content[
### Class `split-main1`
]]

.row[.content[
]]

.row[
]

---
class: split-main2 with-thick-border border-black

.row[.content[
### Class `split-main2`
]]

.row[.content[
]]

.row[.content.center[
]]

.row[
]

---
class: split-main2 with-thick-border border-black

.row[.content[
### Class `split-main2` with `split-two` on third row
]]

.row[.content[
]]

.row[.content[
.split-two[
.column[
]
.column.center[.content[
]]
]
]]

.row[
]