---
pagetitle: "Ninjutsu hacking"
output:
  xaringan::moon_reader:
    css: [default, ninjutsu, custom.css, custom-fonts.css]
    lib_dir: libs
    seal: false
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
layout: true

```{r, include=FALSE}
library(dplyr)
library(knitr)
library(ggplot2)
library(icon)
```

```{r, echo=FALSE, fig.width=15, fig.height=3}
plot <- ggplot(iris, aes(Sepal.Width, Sepal.Length, colour = Species)) +
  geom_point()
```

---
class: split-title hide-slide-number

.row[.content[
# `r fa("user-ninja", size = 3)`
]]

.row[.content[
  # Ninja scaffolding
  ## Splitting [{xaringan}](https://slides.yihui.org/xaringan/#1) slides into sections
  ### Adapting [Emi Tanaka](https://emitanaka.org/)'s [Ninjutsu](https://emitanaka.org/ninja-theme/themes/kunoichi/kunoichi-theme-example.html#7)
  
  `r fa('twitter')` [mattdray](https://twitter.com/mattdray)
  `r fa('github')` [matt-dray](https://github.com/matt-dray)
  `r fa('globe')` [rostrum.blog](https://www.rostrum.blog/) 
]]

---
class: split-main1

.row[.content[
  ### A page with title and footer bars
]]

.row[.content[
```{r, echo=FALSE, fig.width=16}
print(plot)
```
]]

.row[.content[
  Footer
]]

---
class: split-main2

.row[.content[
  ### This page has _two_ rows in the body area
]]

.row[.content[
This slide is split into four rows that are all 100% of the width of the page:

* the title and footer bars
* two rows in the main body (text in this one, plot in the one below)
]]

.row[.content.center[
```{r, echo=FALSE, fig.width=15, fig.height=3}
print(plot)
```
]]

.row[
  Footer
]

---
class: split-main2

.row[.content[
  ### The lower body row is now split vertically!
]]

.row[
Here is some text for this row that stretches aaaaall the way across the page and wraps down to the next line.
]

.row[.content[
.split-two[
  .column[
`r kable(head(iris), format="html")`
  ]
  .column.center[
`r fa("r-project", size = 5)` 
  ]
]
]]

.row[
  Footer
]